Compiling refinement types to dependent types

### 2020-07-18 tex/paper.tex
More instances of old \mu_ things

We translate the surface language contexts, types and terms into the corresponding core language entities
using the $\mu_\Gamma$, $\mu_\tau$ and $\mu_\varepsilon$ functions respectively,
which are defined mutually recursively.

>>>>

We translate the surface language contexts, types and terms into the corresponding core language entities
using the $\tranctx$, $\tranty$ and $\tranterm$ functions respectively,
which are defined mutually recursively.
